### 2014-08-29 paper/paper.Rmd
first pass at TV section

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
library(dplyr)
library(stringr)
library(stringr)
library(reshape2)
library(ggplot2)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(rworldmap)
library (grid)    
library (scales)
library(doBy)
```

@@

```{r dataprep, echo = FALSE, message = FALSE, warning = FALSE}
colnames(student2012)[1] <- "name"
student2012$name <- as.character(student2012$name)
colnames(school2012)[1] <- "name"
school2012$name <- as.character(school2012$name)

fix_country = function(df) {
df$name = as.character(df$name)
df$name[df$name=="Serbia"] <- "Republic of Serbia"
df$name[df$name=="Korea"] <- "South Korea"
df$name[df$name=="Chinese Taipei"] <- "Taiwan"
df$name[df$name=="Slovak Republic"] <- "Slovakia"
df$name[df$name=="Russian Federation"] <- "Russia"
df$name[df$name=="Perm(Russian Federation)"] <- "Russia"
df$name[df$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
df$name[df$name=="China-Shanghai"] <- "China"
df$name[df$name=="China-Macau"] <- "China"
df$name[df$name=="Connecticut (USA)"] <- "United States of America"
df$name[df$name=="Florida (USA)"] <- "United States of America"
df$name[df$name=="Massachusetts (USA)"] <- "United States of America"

df
}

# Now add data
#student2012$name[student2012$name=="Serbia"] <- "Republic of Serbia"
#student2012$name[student2012$name=="Korea"] <- "South Korea"
#student2012$name[student2012$name=="Chinese Taipei"] <- "Taiwan"
#student2012$name[student2012$name=="Slovak Republic"] <- "Slovakia"
#student2012$name[student2012$name=="Russian Federation"] <- "Russia"
#student2012$name[student2012$name=="Perm(Russian Federation)"] <- "Russia"
#student2012$name[student2012$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
#student2012$name[student2012$name=="China-Shanghai"] <- "China"
#student2012$name[student2012$name=="China-Macau"] <- "China"
#student2012$name[student2012$name=="Connecticut (USA)"] <- "United States of America"
#student2012$name[student2012$name=="Florida (USA)"] <- "United States of America"
#student2012$name[student2012$name=="Massachusetts (USA)"] <- "United States of America"
student2012$ST06Q01 <- as.numeric(student2012$ST06Q01)
student2012$PV1MATH <- as.numeric(student2012$PV1MATH)
student2012$PV1READ <- as.numeric(student2012$PV1READ)
student2012$PV1SCIE <- as.numeric(student2012$PV1SCIE)
student2012$SENWGT_STU <- as.numeric(student2012$SENWGT_STU)

school2012 = fix_country(school2012)
student2012 = fix_country(student2012)
```

### Teachers, computers, and libraries at school make a difference in math scores

```{r shortages, echo = FALSE, message = FALSE, warning = FALSE}
school2012.sub = school2012[, c(1, 6, 34, 35, 40, 45, 46, 47, 48, 49, 50, 51)] #%>% select(name, SCHOOLID, SC11Q02, SC11Q03, SC14Q02, SC14Q07, SC14Q08, SC14Q09, SC14Q10, SC14Q11, SC14Q12, SC14Q13)
student2012.sub = student2012[, c(1, 6, 501, 541, 546, 634)] #%>% select(name, SCHOOLID, PV1MATH, PV1READ, PV1SCIE)

scores_by_school = summarise(group_by(student2012.sub, name, SCHOOLID), mmath = mean(PV1MATH), 
                                      mread = mean(PV1READ), msci = mean(PV1SCIE))

df = scores_by_school %>% left_join(school2012.sub)
df2 <- summarise(group_by(df, name, SC14Q02), mmath2 = mean(mmath))
qplot(SC14Q02, mmath2, data = df2, facets = ~name)
df3 <- summarise(group_by(df, name, SC14Q10), mmath2 = mean(mmath))
qplot(SC14Q10, mmath2, data = df3, facets = ~name)
```

@@

***Need to get this code working

```
# Out of School Study time
b1 <- summaryBy(data=student2012, pvM + pvR + pvS+ ST57Q01+ ST57Q02 +ST57Q03+ ST57Q04+ ST57Q05+ ST57Q06 ~CNT,FUN=mean, na.rm=T)
names(b1) <- c("CNT","pvM","pvR","pvS","ST57Q01", "ST57Q02","ST57Q03", "ST57Q04", "ST57Q05", "ST57Q06" )
# Out of school study time (total hours HW)
b1$CNT <- reorder(factor(b1$CNT),b1$pvS, mean)
b2 <- melt(b1[,c("CNT","pvM","pvR","pvS")],id="CNT")
b2 <- cbind(b2, b1[match(b2$CNT,b1$CNT), 5:10])
qplot(CNT, value,color=variable,size=ST57Q01, data = b2)+ coord_flip()
head(b2)
qplot(ST57Q01, value,color=variable,size=ST57Q02, data = b2)+ coord_flip()+facet_wrap(~CNT)

student.sub <- studschool[,c("name","pvM","pvR","pvS","ST57Q01","OECD","SC03Q01")]
study <- melt(student.sub,id=c("name","ST57Q01","OECD","SC03Q01"))
names(study) <- c("Country","HomeworkHours","OECD","AREA","Subject","Score")
levels(study$Subject) <- c("Math","Reading","Science")
p <- ggplot(data = study, aes(HomeworkHours,Score,colour=Subject) )+xlim(0,20)+facet_wrap(~Country)+stat_smooth(se=F)+ xlab("Out-of-School Study Hours")
#ggsave(p,file="studytime.pdf",height=13,width=13)
p <- ggplot(data=student.sub, aes(ST57Q01, ..density..)) + geom_histogram(binwidth=5) + xlab("Out-of-School Study Hours") +xlim(0,30)
ggsave(p,file="HistHWschool.pdf",width=8,height=6)

student.sub <- studschool[,c("name","pvM","ST57Q01","SC03Q01")]
study <- student.sub
names(study) <- c("Country","Math","HomeworkHours","Schoolplace")

p <- ggplot(data = study, aes(HomeworkHours,Math,colour=Schoolplace) )+xlim(0,20)+facet_wrap(~Country)+stat_smooth(se=F)
#ggsave(p,file="studytime.pdf",height=13,width=13)
p <- ggplot(data=student.sub, aes(ST57Q01, ..density..)) + geom_histogram(binwidth=5) + xlab("Out-of-School Study Hours") + facet_grid(SC03Q01~.) +xlim(0,30)
```
### More TVs yield higher math scores in the developing world, but lower in the developed countries

@@

Shiny app

@@

Software packages

>>>>

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
library(dplyr)
library(stringr)
library(stringr)
library(reshape2)
library(ggplot2)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(htmltools)
library(rworldmap)
library (grid)    
library (scales) 
```

@@

```{r dataprep, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
colnames(student2012)[1] <- "name"
# Now add data
student2012$name <- as.character(student2012$name)
student2012$name[student2012$name=="Serbia"] <- "Republic of Serbia"
student2012$name[student2012$name=="Korea"] <- "South Korea"
student2012$name[student2012$name=="Chinese Taipei"] <- "Taiwan"
student2012$name[student2012$name=="Slovak Republic"] <- "Slovakia"
student2012$name[student2012$name=="Russian Federation"] <- "Russia"
student2012$name[student2012$name=="Perm(Russian Federation)"] <- "Russia"
student2012$name[student2012$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012$name[student2012$name=="China-Shanghai"] <- "China"
student2012$name[student2012$name=="China-Macau"] <- "China"
student2012$name[student2012$name=="Connecticut (USA)"] <- "United States of America"
student2012$name[student2012$name=="Florida (USA)"] <- "United States of America"
student2012$name[student2012$name=="Massachusetts (USA)"] <- "United States of America"
student2012$ST06Q01 <- as.numeric(student2012$ST06Q01)
student2012$PV1MATH <- as.numeric(student2012$PV1MATH)
student2012$PV1READ <- as.numeric(student2012$PV1READ)
student2012$PV1SCIE <- as.numeric(student2012$PV1SCIE)
student2012$SENWGT_STU <- as.numeric(student2012$SENWGT_STU)
```

### Teachers, computers, and libraries at school matter

@@

### More TVs yield higher math scores in the developing world, but lower in the developed countries

One of the factors in the PISA 2012 dataset is the number of televisions in the student's household. In the dataset, possible values were: "zero", "one", "two", or "three or more". Because there were so (relatively) few observations of "zero", for this invesitgation, the "zero" and "one" categories were combined to form a "one or less" category.

A linear regression as made for the students of each country, using the math score as the dependent variable and the number of televisions as the independent variable (as an ordered factor). Using R's `lm()` function, the direction and significance of the correlation was determined for each country. Significance is indicated by the p-value for a given regression being less than the popular 0.05.

For many countries, a significant relationship was be found between math scores and number of household televisions. The interesting part was to notice that those countries with a significant *positive* relationship appear to include much of the developing world (with lower median-scores), while those countries with a significant *negative* relationship appear to include much of the developed world (with higher median-scores).

Although results shown here are for math only, a similar set of relationships is found using the reading and science scores.

It seems that television is a great equalizer.

```{r place_map_countries, echo=FALSE}
tags$div(
  style = "height: 400px",
  tags$p(
    tags$img(
      align = "right",
      src = "img/ijl_map.png",
      style="max-height: 100%"
    ),
    tags$img(
      align = "left",
      src = "img/ijl_countries.png",
      style="max-height: 100%"
    )
  )
)
```

Find your own correlations: http://bit.ly/pisa2012_explorer

@@

The PISA dataset contains dozens of household factors; we wanted a way to make our data-exploration more efficient. Moreover, we wanted a way that we could make explorations independent of each other, as during the course of the invesigation our team was in three cities over two hemispheres.

To make our exploration easier, we developed a "Shiny" app.

Shiny is a open-source tool, developed by RStudio, that allows an investigator to create a web-based appication powered by R.

@@

Shiny, by RStudio

plyr, dplyr, and ggplot2, by Hadley Wickham
